Code for Breast Cancer Pain Study

### 2020-08-05 manuscript_code_20200728.Rmd
figures updated

## Table 1

@@

@@

@@

@@

# points(x=meandata$Poverty,y=meandata$Pain,
#        cex=cex,lwd=1.5)
x=seq(0,70,by=1)
points(x=x,y=fhat(x),type="l",lwd=3,
       col=brewer.pal(n=9,"YlOrRd")[7])
dev.off()

@@

@@

x=seq(0,53,by=1)
points(x=x,y=fhat(x),type="l",lwd=3,
       col=brewer.pal(n=9,"YlOrRd")[7])
dev.off()

>>>>

## Table 1 (Base)

@@

```{r,echo=FALSE}
explvars = c("Pain","Poverty","Blight",
             "Occupation","Marital.status","Insurance.type",
             "Cancer.stage","Chemo","Surgery",
             "Race","Age")

table.sum1 = cbind(do.call("rbind",sapply(1:length(explvars),get_summary)),
                   do.call("rbind",sapply(1:length(explvars),get_mean)),
                   do.call("rbind",sapply(1:length(explvars),get_pval)))
colnames(table.sum1) = c("No. (%)","Pain, mean [Q1,Q3]","P-value")

## Table 1 (Base + more biomarker variables)

@@

## Scatter plots

@@

x=seq(0,70,by=1)
yy.pred = predict(p.glm, data.frame(Poverty=x), type="link", se=T)
yy = exp(yy.pred$fit)
yy.upper = exp(yy.pred$fit + 1.96*yy.pred$se)
yy.lower = exp(yy.pred$fit - 1.96*yy.pred$se)

@@

# points(x=meandata$Poverty,y=meandata$Pain,
#        cex=cex,lwd=1.5)
points(x=x,y=yy,type="l",lwd=3,
       col=brewer.pal(n=9,"YlOrRd")[7])
polygon(c(x,rev(x)), c(yy.upper,rev(yy.lower)), col="#FF000050", border=NA)

legend("bottomright",bty="n",cex=1.5,
       legend=c(paste("exp(coef) =",round(exp(p.glm$coefficients[2]),digits=2)),
                paste("(P-value < .001)"),
                paste("")))

dev.off()

@@

x=seq(0,60,by=1)
yy.pred = predict(p.glm, data.frame(Blight=x), type="link", se=T)
yy = exp(yy.pred$fit)
yy.upper = exp(yy.pred$fit + 1.96*yy.pred$se)
yy.lower = exp(yy.pred$fit - 1.96*yy.pred$se)

@@

points(x=x,y=yy,type="l",lwd=3,
       col=brewer.pal(n=9,"YlOrRd")[7])
polygon(c(x,rev(x)), c(yy.upper,rev(yy.lower)), col="#FF000050", border=NA)

legend("bottomright",bty="n",cex=1.5,
       legend=c(paste("exp(coef) =",round(exp(p.glm$coefficients[2]),digits=2)),
                paste("(P-value < .001)"),
                paste("")))
dev.off()
